Effect_size_families

### 2020-06-26 Thesis_Chapter_1/Supp_Material.Rmd
Supplementary

__Figure S5.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.

__Figure S6.__ Violin plot of the reproductive biology of the species.

__Figure S7.__ Grouped effect sizes by family for each recipient species.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
library(ggplot2)
setwd("~/R_projects/Hp_pollen_experiment")
total_pollen <- read.csv("Data/Csv/total_pollen.csv")
ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
  geom_bar(stat='identity', position='dodge')+theme_minimal()+
  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
par(mar=c(30,13,2,4),xpd=F)
setwd("~/R_projects/Hp_pollen_experiment")
data_percentage <-readRDS("Data/RData/per.RData")
data_percentage=as.matrix(data_percentage)
coul = c("#999999","#779799")
barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
 "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
abline(v=50,col="black")

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
par(mar=c(2,13,2,4),xpd=F)
par(mfrow=c(3,1))
setwd("~/R_projects/Hp_pollen_experiment")
ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E. sativa-I. purpurea", "B. oleracea-I. purpurea","B. rapa-I. purpurea", "S. alba-I. aquatica", "S. alba-S. melongena", "E. sativa-P. integrifolia", "B. rapa-S. lycopersicum", "B. oleracea-C. annuum"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(8.3,6.8,"A) Brassicaceae")
ratio_con <-readRDS("Data/RData/ratio_con.RData")
barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I. purpurea-S. melongena","I. aquatica-C. annuum","I. purpurea-E. sativa","I. aquatica-S. alba"))
abline(v=50,col="black")
legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(9,3.5,"B) Convolvulaceae")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, fig.align='center', fig.cap="Fig S5"}

@@

par(mfrow=c(2,2))
ggplot(CLD,aes(x= fam_foc,y= lsmean,
               label = .group)) +theme_ms()+
  geom_point(shape  = 15,size   = 4) +ggtitle("")+
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
                width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+ geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(axis.text.x = element_text(size=14, face="bold"))

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, out.width = "100%", fig.align='center', fig.cap="Fig S6"}
setwd("~/R_projects/Hp_pollen_experiment")

#Script to plot the reproductive biology tests
#load libraries
library(ggplot2)
#install.packages("devtools")
library(devtools)
#install_github("easyGgplot2", "kassambara")

@@

rep_bio <- ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
  geom_violin(scale = "width",draw_quantiles = c(0.5))+
  geom_dotplot(binaxis='y', 
               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(legend.title = element_blank(),plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))

rep_bio
 #pdf("test.pdf", width = 12, height = 5)

 #ggsave("Images_publication/Figure2.png", width = 12, height = 5,dpi = 1200)

ggsave(filename = "rep_bio.pdf", rep_bio, width = 12, height = 5, units = "in",dpi = 1000)

# insert ggplot code
dev.off()

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="S7"}

>>>>

__Figure S5.__ Unipartite bidirectional network with asymmetrical effect

__Figure S6.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.

__Figure S7.__ Violin plot of the reproductive biology of the species.

__Figure S8.__ Grouped effect sizes by family for each recipient species.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S2"}
library(ggplot2)
setwd("~/R_projects/Hp_pollen_experiment")
total_pollen <- read.csv("Data/Csv/total_pollen.csv")
ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
  geom_bar(stat='identity', position='dodge')+theme_minimal()+
  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="Fig S3"}
par(mar=c(30,13,2,4),xpd=F)
setwd("~/R_projects/Hp_pollen_experiment")
data_percentage <-readRDS("Data/RData/per.RData")
data_percentage=as.matrix(data_percentage)
coul = c("#999999","#779799")
barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
 "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
abline(v=50,col="black")

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S4"}
par(mar=c(2,13,2,4),xpd=F)
par(mfrow=c(3,1))
setwd("~/R_projects/Hp_pollen_experiment")
ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E. sativa-I. purpurea", "B. oleracea-I. purpurea","B. rapa-I. purpurea", "S. alba-I. aquatica", "S. alba-S. melongena", "E. sativa-P. integrifolia", "B. rapa-S. lycopersicum", "B. oleracea-C. annuum"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(8.3,6.8,"A) Brassicaceae")
ratio_con <-readRDS("Data/RData/ratio_con.RData")
barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I. purpurea-S. melongena","I. aquatica-C. annuum","I. purpurea-E. sativa","I. aquatica-S. alba"))
abline(v=50,col="black")
legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(9,3.5,"B) Convolvulaceae")

@@

\clearpage

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig. S4** Pollen ratios comparisons between the different pollen recipient families where the boxes represent least square means, the error bars, confidence intervals 95%, and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons). These pollen ratios are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen), and then compared by family (N=20)."}

@@

ggplot(CLD,aes(x= fam_foc,y= lsmean,
               label = .group)) +theme_ms()+
  geom_point(shape  = 15,size   = 4) +ggtitle("")+
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
                width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+ geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(axis.text.x = element_text(size=14, face="bold"))

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig. S5** Unipartite bidirectional network with asymmetrical effect. The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species. All the arrow heads point to the recipient species of the reciprocal interaction. Lines of species that did not have a negative impact are not represented. The different nodes and the donor species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green). The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size. Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}
library(statnet)
library(reshape2)
library(sna)
library(igraph)
setwd("~/R_projects/Hp_pollen_experiment")

#######################################
############ Data preparataion ########
#######################################

#In this script I'm going to plot the transitivity of the effect oh HP pollen with effect sizes
effect <- readRDS("Data/RData/matrix_effect_size.RData")
#Now I convert the few values over 0 to maximum 0 (control)
effect[effect>0]<-0
#absolute values so less confusing without negative values
#So now greater values involve greater effect
#(opposite way in comparison with negative values as before)
effect=abs(effect)
#UNIPARTITE DOUBLE ASSYMETRICAL EFFECT
G <- graph.adjacency(t(effect),weighted=TRUE,diag=FALSE)
#plot(G)
E <- t(apply(get.edgelist(G),1,sort))
E(G)$curved <- 0
E(G)[duplicated(E) | duplicated(E,fromLast =TRUE)]$curved <- 0.2
plot(G, edge.width=E(G)$weight/0.5,  vertex.color=c(rep("#0072B2",2),"#D55E00","#0072B2", rep("#009E73",2),
              "#D55E00","#0072B2", rep("#D55E00",2)),edge.arrow.size=0.8,edge.color=adjustcolor(c(rep("#0072B2",8),rep("#0072B2",8), rep("#D55E00",7), 
              rep("#0072B2",9),rep("#009E73",7),rep("#009E73",9),rep("#D55E00",7),rep("#0072B2",8), rep("#D55E00",8), rep("#D55E00",7)), alpha.f = .5))

\clearpage

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig S6** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment. Positive correlations are displayed in blue and negative in red. The intensity, size and colour of the circles are proportional to the correlation coefficient from Pearson’s r."}
#install.packages("corrplot")
library(corrplot)
setwd("~/R_projects/Hp_pollen_experiment")
#Example
#I'm going to try to show our traits on this way
#M <- cor(mtcars)
#corrplot(M, method = "circle")
#We can kill two birds with one stone, showing the correlation and all the traits
traits_all <- read.csv("Data/Csv/traits_all.csv")
si_index <- readRDS("Data/RData/si_index.RData")
traits_all$si_index <- si_index
traits_all=traits_all[,-c(1,2)]
traits_all=traits_all[,-c(1,7,11)]
#Change order of ovary width length I rename below in row and colname
a<-traits_all[,11]
b<-traits_all[,12]
traits_all[,11] <-b
traits_all[,12]<- a
traits_all<- cor(traits_all)

rownames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
                         "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
                         "Ovary length", "Ovary width", "SI index")

colnames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
                "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
                "Ovary length", "Ovary width", "SI index")

#corrplot(traits_all, method = "circle")
#corrplot(traits_all, type = "upper")
par(mar=c(0,4.1,4.1,2.1))
corrplot(traits_all, type = "lower", tl.cex = 0.8, cl.cex = 0.8, tl.col = "black", tl.srt = 45)

#Add Compatibility index!

\clearpage

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig. S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments (apomixis, hand cross pollination, hand self pollination and spontaneous selfing). The coloured dots, represent the different values of seed set for each treatment."}

setwd("~/R_projects/Hp_pollen_experiment")

#Script to plot the reproductive biology tests
#load libraries
library(ggplot2)
#install.packages("devtools")
library(devtools)
#install_github("easyGgplot2", "kassambara")
library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

@@

 ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
  geom_violin(scale = "width",draw_quantiles = c(0.5))+
  geom_dotplot(binaxis='y', 
               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(legend.title = element_blank(),plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="**Fig. S8** Effect sizes (95% confidence intervals) of the different families on each focal species (recipient) and a hand cross-pollination treatment (control). For each species the control treatment appears in yellow and the grouped effect per family in blue for Brassicaceae, green for Convolvulaceae and orange for Solanaceae."}

### 2020-06-26 Thesis_Chapter_1/Supp_Material.tex
Supplementary

\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
pollen donor and recipient.

\textbf{Figure S6.} Violin plot of the reproductive biology of the
species.

\textbf{Figure S7.} Grouped effect sizes by family for each recipient
species.

@@

\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}

@@

\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}

@@

\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}

@@

\begin{figure}

{\centering \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-7-1}

}

\caption{Fig S5}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{Supp_Material_files/figure-latex/unnamed-chunk-8-1}

}

\caption{Fig S6}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{verbatim}
## null device 
##           1
\end{verbatim}

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{S7}
\end{figure}

>>>>

\textbf{Figure S5.} Unipartite bidirectional network with asymmetrical
effect

\textbf{Figure S6.} Statistical comparison of pollen ratios by family as
pollen donor and recipient.

\textbf{Figure S7.} Violin plot of the reproductive biology of the
species.

\textbf{Figure S8.} Grouped effect sizes by family for each recipient
species.

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Fig S2}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Fig S3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Fig S4}
\end{figure}

\clearpage

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{\textbf{Fig. S4} Pollen ratios comparisons between the
different pollen recipient families where the boxes represent least
square means, the error bars, confidence intervals 95\%, and sharing
numbers indicate no significant differences between groups (Tukey
adjusted comparisons). These pollen ratios are the total number of
heterospecific pollen grains divided by the total quantity of pollen
(conspecific pollen + heterospecific pollen), and then compared by
family (N=20).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\textbf{Fig S5} Unipartite bidirectional network with
asymmetrical effect. The lines with the arrow heads connect the impact
of foreign pollen (effect size) of each pollen donor species on each
recipient species. All the arrow heads point to the recipient species of
the reciprocal interaction. Lines of species that did not have a
negative impact are not represented. The different nodes and the donor
species appear coloured by family: Solanaceae (orange), Brassicaceae
(blue) and Convolvulaceae (green). The intensity of the effect is
represented by the line´s size where a larger effect size corresponds to
a thicker line and a thinner line to a smaller effect size. Species
code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa,
SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea,
CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum
lycopersicum, SOME: Solanum melongena.}
\end{figure}

\clearpage

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\textbf{Fig S6} Graphical representation of the correlation
matrix of the different reproductive traits considered in the
experiment. Positive correlations are displayed in blue and negative in
red. The intensity, size and colour of the circles are proportional to
the correlation coefficient from Pearson's r.}
\end{figure}

\clearpage

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{\textbf{Fig. S7} Violin plot of the proportion of seeds
coverted to ovule (\%) for all species with four different
hand-pollination treatments (apomixis, hand cross pollination, hand self
pollination and spontaneous selfing). The coloured dots, represent the
different values of seed set for each treatment.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{\textbf{Fig. S8} Effect sizes (95\% confidence intervals) of
the different families on each focal species (recipient) and a hand
cross-pollination treatment (control). For each species the control
treatment appears in yellow and the grouped effect per family in blue
for Brassicaceae, green for Convolvulaceae and orange for Solanaceae.}
\end{figure}
